---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# StoXreader

<!-- badges: start -->
<!-- badges: end -->

The primary goal of StoXreader is to smoothly import and combine public StoX
estimate reports from the Institute of Marine Research, available at:
https://www.hi.no/hi/forskning/marine-data-forskningsdata/bestandovervakning.
The package also includes simple functions to visualize weight-at-age by year
or stratum.

A data frame from Barents Sea Northeast Arctic cod bottom trawl index in winter
is included in this package and contains data from 1999 to 2019. This can be
used for data exploration and visualization.

## Installation

You can install the development version of StoXreader from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("amalieepaulsen/StoXreader")
```
## About read_stox()

read_stox() is the primary import function in the StoXreader package. StoX
data folders downloaded from IMR's website contain three text files in
~/output/baseline/report. These files are estimate reports on abundance,
biomass, and mean weight. They all contain tables with length groups and age,
and are separated by stratum. read_stox() is a function that can import any
three StoX files with the same format as long as the file names are unchanged.

## Examples

The text files in the example have been downloaded from:
https://metadata.nmdc.no/metadata-api/landingpage/4abaafc79163a4ffed0b2ec7f2aca002.

```{r example1}
library(StoXreader)

a_path <- system.file(
  "extdata/stox_winter_2019/2_EstimateByPopulationCategory_Reports_Abundance.txt",
  package = "StoXreader")
b_path <- system.file(
  "extdata/stox_winter_2019/2_EstimateByPopulationCategory_Reports_Biomass.txt",
  package = "StoXreader")
w_path <- system.file(
  "extdata/stox_winter_2019/2_EstimateByPopulationCategory_Reports_MeanWeight.txt",
  package = "StoXreader")

head(read_stox(a_path, b_path, w_path))
```
